rawPaper

### 2020-10-21 analysis/paper/rawPaper.Rmd
var names changed-rest as before

getNames <- strsplit(names(fastafile), '_')         # creating a vector splitting species names
removeSeqs <- c("sp.")                              # finding names to remove: indexes which are in the species to be removed
keepSeqs <- which(! getNames %like% removeSeqs)     # selection those without specific name in them

# saving a new fasta file with only those seqs with full scientific names
write.fasta(sequences=fastafile[keepSeqs], names=names(fastafile)[keepSeqs], file.out="Sicydium_COI_edits.fasta")

>>>>

fastaNames <- strsplit(names(fastafile), '_')                  # creating a vector splitting species names
incompleteNames <- c("sp.")                                    # finding names to remove: indexes which are in the species to be removed
completeSeqs <- which(! fastaNames %like% incompleteNames)     # selection those without specific name in them

# saving a new fasta file with only those seqs with full scientific names
write.fasta(sequences=fastafile[completeSeqs], names=names(fastafile)[completeSeqs], file.out="Sicydium_COI_edits.fasta")
